---
title: "EPLC analysis"
author: "Jacob W. Roden-Foreman"
date: "`r Sys.time()`"
runtime: shiny
output:
  html_document:
    pandoc_args: "--dpi=150"
    fig_height: 3
    fig_width: 5
    code_folding: show
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup and import}
options(kableExtra.auto_format = FALSE) #for proper table formating in Word
knitr::opts_chunk$set(echo = TRUE,
											results = "asis")

library(tidyverse)
library(data.table)
library(fst)
library(bit64)
library(DiagrammeR)


mdata = read_fst("Data/final/final combined dataset.fst")



med_iqi = function(x, w=mdata$discwt, na.rm=T, digits=2){
	
	digits = as.character(digits)
	
	fmt = paste0("%.", digits, "f [%.", digits, "f, %.", digits, "f]")
	
	if(is.null(w)){
		sprintf(fmt,
						quantile(x=x, probs = 0.5, na.rm = na.rm), 
						quantile(x=x, probs = 0.25, na.rm = na.rm), 
						quantile(x=x, probs = 0.75, na.rm = na.rm))
	} else{
		sprintf(fmt,
						spatstat::weighted.quantile(x=x, w=w, probs = 0.5, na.rm = na.rm), 
						spatstat::weighted.quantile(x=x, w=w, probs = 0.25, na.rm = na.rm), 
						spatstat::weighted.quantile(x=x, w=w, probs = 0.75, na.rm = na.rm))
	}
	
}



my.weighted.mean = function(x, w = mdata$discwt, na.rm=T){
	
	weighted.mean(x=x, w = w, na.rm = na.rm)
	
	
}


cat_perc = function(df, x, w = "discwt"){
	
	df = as.data.frame(df)
	x = df[, x]
	w = df[, w]
	rm(df)
	
	res = data.frame(var = unique(x))
	res$n = NA_real_
	res$perc = NA_real_
	total = sum(w, na.rm = T)
	
	for(i in 1:nrow(res)){
		res$n[i] = round( sum( w[x==res$var[i] ], na.rm = T ) )
	}
	
	res$var = as.character(res$var)
	res = res[!is.na(res$var), ]
	res = rbind(res, c("Missing", round(sum(w[ is.na(x) ])), NA))
	res$n = as.numeric(res$n)
	res$perc = round((res$n/total)*100, 2)
	
	
	res
	
}

cat_perc_by = function(df, groups, wt_var = "discwt"){
	
	plyr::count(df, groups, wt_var = wt_var) %>% 
	group_by_(groups[1]) %>% 
	mutate(perc = round((freq/sum(freq))*100, 2) ) %>% 
	ungroup() %>% 
	mutate(val = paste0(format(round(freq), big.mark = ","), " (", perc, "%)")) %>% 
	select(-freq, -perc) %>% 
	pivot_wider(names_from = groups[1], 
							values_from = val)
	
}





```





```{r add a few new vars}


#add definition for high risk vs. not -----
high_risk_codes = readxl::read_excel("high-risk_ecodes.xlsx",
																		 sheet = "ICD-9"
																		 )

#remove periods
high_risk_codes$ecode = str_remove_all(high_risk_codes$ecode, 
																			 fixed("."))


mdata$high_risk = mdata$ecode1 %in% high_risk_codes$ecode

mdata$high_risk[mdata$high_risk == TRUE] = "High-risk"
mdata$high_risk[mdata$high_risk == "FALSE"] = "Non-high-risk"

rm(high_risk_codes)




#pull out trauma center level -----
#NEDS Stratum: 2nd digit – Trauma: 
#(0) Not a trauma center,
#(1) Trauma center level I, 
#(2) Trauma center level II,
#(3) Trauma center level III.
#Collapsed categories used for strata with small sample sizes: 
#(4) Nontrauma center or trauma center level III, 
#(8) Trauma center level I or II. 


mdata$hosp_trauma_level = case_when(
	substring(mdata$neds_stratum, 2, 2) == 1 ~ "Trauma center level I",
	substring(mdata$neds_stratum, 2, 2) == 2 ~ "Trauma center level II",
	substring(mdata$neds_stratum, 2, 2) == 3 ~ "Trauma center level III",
	TRUE ~ "All Other Hospitals") %>% 
	factor(., 
				 levels = c("Trauma center level I", 
				 					 "Trauma center level II",
				 					 "Trauma center level III",
				 					 "All Other Hospitals"),
				 ordered = TRUE)







#add injury dx flags ----

dx = read_fst("Data/final/dx_final.fst",
							columns = c("key_ed", "dx1"))
source("icd9_to_Barell.R")

bar = icd9_to_barrel(dx$dx1)

all.equal(as.integer64(mdata$key_ed), as.integer64(dx$key_ed))


# Brain Injury: 850-854
mdata$injury_brain = dx$dx1 %in% as.character(85000:85499)

# Skull Fracture: 800-804
mdata$injury_skull_fx = dx$dx1 %in% as.character(80000:80499)

# Cervical Spine Fracture
mdata$injury_cspine = bar$region_3 %in% c("CERVICAL VCI", "CERVICAL SCI")

# Rib or Sternum Fracture: 809
mdata$injury_rib_fx = dx$dx1 %in% as.character(80900:80999)

# Cardiac or Pulmonary Injury: 860-861
mdata$injury_cardio_pulm = dx$dx1 %in% as.character(86000:86199)

# Thoracic Spine Fracture
mdata$injury_tspine = bar$region_3 %in% c("THORACIC/DORSAL VCI", "THORACIC/DORSAL SCI")

# Lumbar Spine Fracture
mdata$injury_lspine = bar$region_3 %in% c("THORACIC/DORSAL VCI", "THORACIC/DORSAL SCI")


# Solid Abdominal Organ Injury
mdata$injury_solid_abd = dx$dx1 %in% as.character(c( 86400:86699, #liver, spleen, kidneys
																										 86381:86384, #pancreas
																										 86391:86394  #pancreas
																										 ))

# Hollow Viscera Injury
mdata$injury_hollow_abd = dx$dx1 %in% as.character(c( 86300:86380, #stomach, intestines
																											86389, 86390, 86399, #other GI
																											86700:86799 #bladder, ureter, urethra
																										 ))




# Upper Extremity Fracture
mdata$injury_ue_fx = bar$dx_type %in% "FRACTURES" & bar$region_2 %in% "UPPER EXTREMITY"

# Pelvis Fracture: 808
mdata$injury_pelvic_fx = dx$dx1 %in% as.character(80800:80899)

# Lower Extremity Fracture
mdata$injury_le_fx = bar$dx_type %in% "FRACTURES" & bar$region_2 %in% "LOWER EXTREMITY"

rm(bar, dx)




# a little recoding
mdata$year_whole = mdata$year %>% substr(., 1, 4) %>% as.integer()

mdata$pay1_recode = case_when(
	mdata$pay1 == "Medicare" | mdata$pay1 == "Medicaid" ~ "Medicare/Medicaid",
	TRUE ~ as.character(mdata$pay1)
) %>% as.factor()





```



\
\
\
\

# CONSORT Flow Chart
```{r}

mdata = filter(mdata, !is.na(mortality))
mdata = filter(mdata, !is.na(totchg))
n = nrow(mdata)
cat("N_obs removing missing mortality, total charges = ", 
		format(n, big.mark=","), "\n", file="nobs log.txt", append=T)


pt_counts = read_lines("nobs log.txt") %>%
	str_split_fixed(., " = ",  n=2) %>% 
	as.data.frame()

pt_counts$V2 = trimws(pt_counts$V2)

pt_counts = pt_counts[pt_counts$V1 != "N_obs after all filters", ]


pt_counts$n = str_remove_all(pt_counts$V2, ",") %>% as.numeric()
pt_counts$n_change = lag(pt_counts$n, 1) - pt_counts$n
pt_counts$n_change = prettyNum(pt_counts$n_change, big.mark = ",")



pt_counts = rbind(pt_counts, 
									c("N_obs after all filters", format(nrow(mdata), big.mark = ","),  nrow(mdata), NA ))


pt_counts$label = c("Number of encounters in NEDS dataset, 2010-2016",
										"Principal diagnosis of trauma",
										"Age \u2265 50 years",
										"Principal external cause of injury not one of burns,\nbites/stings, overexertion, poisoning, or\nmisadventures of medical/surgical care",
										"Not missing data for mortality or total charges",
										"Included for analysis"
)





DiagrammeR::grViz("
digraph graph2 {

graph [layout = dot, rankdir = TB]

# node definitions with substituted label text
node [shape = rectangle, width = 4, fillcolor = Biege]
a [label = '@@1']
b [label = '@@2']
c [label = '@@3']
d [label = '@@4']
e [label = '@@5']
f [label = '@@6']

b_out [label = '@@7']
c_out [label = '@@8']
d_out [label = '@@9']
e_out [label = '@@10']


a -> b -> c -> d -> e -> f
a -> b_out -> c_out -> d_out -> e_out

}

[1]: paste0(pt_counts$label[1], ': n = ', pt_counts$V2[1])
[2]: paste0(pt_counts$label[2], ': n = ', pt_counts$V2[2])
[3]: paste0(pt_counts$label[3], ': n = ', pt_counts$V2[3])
[4]: paste0(pt_counts$label[4], ': n = ', pt_counts$V2[4])
[5]: paste0(pt_counts$label[5], ': n = ', pt_counts$V2[5])
[6]: paste0(pt_counts$label[6], ': n = ', pt_counts$V2[6])
[7]: paste0('Excluded: n = ', pt_counts$n_change[2])
[8]: paste0('Excluded: n = ', pt_counts$n_change[3])
[9]: paste0('Excluded: n = ', pt_counts$n_change[4])
[10]: paste0('Excluded: n = ', pt_counts$n_change[5])
"
)





```



\
\
\



# Table 1. Characteristics of `r format(nrow(mdata), big.mark=",")` encounters with traumatic injury


```{r}

mdata %>%
	group_by(high_risk) %>% 
	summarise(n_obs = n(),
						n_weighted = round(sum(discwt, na.rm = T)), 
						age = med_iqi(age, w = discwt),
						male = round(my.weighted.mean(female==0, w = discwt)*100, 2),
						elixhauser = med_iqi(elixhauser, w = discwt),
						pDeath = med_iqi(pDeath*100, w = discwt),
						los_ip = med_iqi(los_ip, w = discwt),
						totchg_ed = med_iqi(totchg_ed, w = discwt),
						totchg_ip = med_iqi(totchg_ip, w = discwt),
						totchg = med_iqi(nrp_ip, w = discwt)
	)



cat_perc_by(mdata, c("high_risk", "female"))

cat_perc_by(mdata, c("high_risk", "injury_brain"))

cat_perc_by(mdata, c("high_risk", "injury_skull_fx"))

cat_perc_by(mdata, c("high_risk", "injury_cspine"))

cat_perc_by(mdata, c("high_risk", "injury_rib_fx"))

cat_perc_by(mdata, c("high_risk", "injury_cardio_pulm"))

cat_perc_by(mdata, c("high_risk", "injury_tspine"))

cat_perc_by(mdata, c("high_risk", "injury_lspine"))

cat_perc_by(mdata, c("high_risk", "injury_solid_abd"))

cat_perc_by(mdata, c("high_risk", "injury_hollow_abd"))

cat_perc_by(mdata, c("high_risk", "injury_ue_fx"))

cat_perc_by(mdata, c("high_risk", "injury_pelvic_fx"))

cat_perc_by(mdata, c("high_risk", "injury_le_fx"))

cat_perc_by(mdata, c("high_risk", "pay1_recode"))

cat_perc_by(mdata, c("high_risk", "zipinc_qrtl"))

cat_perc_by(mdata, c("high_risk", "died_visit"))

cat_perc_by(mdata, c("high_risk", "disp_ed"))

cat_perc_by(mdata, c("high_risk", "edevent"))

cat_perc_by(mdata, c("high_risk", "disp_ip"))

cat_perc_by(mdata, c("high_risk", "hosp_trauma_level"))





```


\
\
\
\


# Table 2. High-risk mechanisms of injury by TMPM probability of death, actual mortality, and median total charge  


```{r}

mdata %>%
	group_by(mortality) %>% 
	summarise(n_obs = n(),
						n_weighted = round(sum(discwt, na.rm = T)), 
						age = med_iqi(age, w = discwt),
						male = round(my.weighted.mean(female==0, w = discwt)*100, 2),
						elixhauser = med_iqi(elixhauser, w = discwt),
						pDeath = med_iqi(pDeath*100, w = discwt),
						los_ip = med_iqi(los_ip, w = discwt),
						totchg_ed = med_iqi(totchg_ed, w = discwt),
						totchg_ip = med_iqi(totchg_ip, w = discwt),
						totchg = med_iqi(nrp_ip, w = discwt)
	)



cat_perc_by(mdata, c("mortality", "female"))

cat_perc_by(mdata, c("mortality", "injury_brain"))

cat_perc_by(mdata, c("mortality", "injury_skull_fx"))

cat_perc_by(mdata, c("mortality", "injury_cspine"))

cat_perc_by(mdata, c("mortality", "injury_rib_fx"))

cat_perc_by(mdata, c("mortality", "injury_cardio_pulm"))

cat_perc_by(mdata, c("mortality", "injury_tspine"))

cat_perc_by(mdata, c("mortality", "injury_lspine"))

cat_perc_by(mdata, c("mortality", "injury_solid_abd"))

cat_perc_by(mdata, c("mortality", "injury_hollow_abd"))

cat_perc_by(mdata, c("mortality", "injury_ue_fx"))

cat_perc_by(mdata, c("mortality", "injury_pelvic_fx"))

cat_perc_by(mdata, c("mortality", "injury_le_fx"))

cat_perc_by(mdata, c("mortality", "pay1_recode"))

cat_perc_by(mdata, c("mortality", "zipinc_qrtl"))

cat_perc_by(mdata, c("mortality", "died_visit"))

cat_perc_by(mdata, c("mortality", "disp_ed"))

cat_perc_by(mdata, c("mortality", "edevent"))

cat_perc_by(mdata, c("mortality", "disp_ip"))

cat_perc_by(mdata, c("mortality", "hosp_trauma_level"))

cat_perc_by(mdata, c("mortality", "year_whole"))




```




\
\
\


# Table 3. Characteristics of `r format(nrow(mdata), big.mark=",")` encounters with traumatic injuries from high-risk activities by survival status  

```{r}

```



# Demographics by Injury Mechanism
```{r demos by mech}



mdata %>%
	group_by(mech1) %>%
	summarise(n_obs = n(),
						n_weighted = round(sum(discwt, na.rm = T)), 
						age = med_iqi(age, w=discwt),
						female = round(my.weighted.mean(female, w=discwt)*100, 2),
						mortality = round(my.weighted.mean(mortality, w=discwt)*100, 2),
						pDeath = med_iqi(pDeath*100, w=discwt)) %>% 
	ungroup() %>%
	kableExtra::kable()




plyr::count(mdata,  c("mech1", "died_visit"), wt_var = "discwt") %>% 
	group_by(mech1) %>% 
	mutate(perc = round((freq/sum(freq))*100, 2) ) %>% 
	ungroup() %>% 
	mutate(freq = round(freq)) %>% 
	pivot_wider(names_from = "died_visit", 
							values_from = c("freq", "perc")) %>%
	kableExtra::kable()



plyr::count(mdata,  c("mech1", "disp_ed"), wt_var = "discwt") %>% 
	group_by(mech1) %>% 
	mutate(perc = round((freq/sum(freq))*100, 2) ) %>% 
	ungroup() %>% 
	mutate(freq = round(freq)) %>% 
	pivot_wider(names_from = "disp_ed", 
							values_from = c("freq", "perc")) %>%
	kableExtra::kable()





plyr::count(mdata,  c("mech1", "edevent"), wt_var = "discwt") %>% 
	group_by(mech1) %>% 
	mutate(perc = round((freq/sum(freq))*100, 2) ) %>% 
	ungroup() %>% 
	mutate(freq = round(freq)) %>% 
	pivot_wider(names_from = "edevent", 
							values_from = c("freq", "perc")) %>%
	kableExtra::kable()




plyr::count(mdata,  c("mech1", "disp_ip"), wt_var = "discwt") %>% 
	group_by(mech1) %>% 
	mutate(perc = round((freq/sum(freq))*100, 2) ) %>% 
	ungroup() %>% 
	mutate(freq = round(freq)) %>% 
	pivot_wider(names_from = "disp_ip", 
							values_from = c("freq", "perc")) %>%
	kableExtra::kable()




plyr::count(mdata,  c("mech1", "age_group"), wt_var = "discwt") %>% 
	group_by(mech1) %>% 
	mutate(perc = round((freq/sum(freq))*100, 2) ) %>% 
	ungroup() %>% 
	mutate(freq = round(freq)) %>% 
	pivot_wider(names_from = "age_group", 
							values_from = c("freq", "perc")) %>%
	kableExtra::kable()










```



\
\
\



After applying the inclusion/exclusion criteria, we will first empirically estimate the median TMPM injury severity for each group of injury mechanisms as defined by the External Causes of Injury for the International Classification of Diseases Ninth and Tenth Revisions, Clinical Modifications (ICD-9-CM and ICD-10-CM, respectively). 

Then, we will rank-order the ten most severe mechanisms of injury by median injury severity value, the probability of death due exclusively to anatomic injuries, as computed using the Trauma Mortality Prediction Model (TMPM) for the ICD-9-CM and ICD-10-CM lexicons, as appropriate.  


```{r rank mechanisms of injury by median pDeath}




res = mdata %>%
	group_by(mech1) %>%
	summarise(n_obs = n(),
						n_weighted = round(sum(discwt, na.rm = T)), 
						pDeath = med_iqi(pDeath*100, w = discwt, digits = 4)) %>%
	ungroup() %>% 
	arrange(desc(pDeath))


res$rank = 1:nrow(res)
res = res[, c("rank", "mech1", "n_obs", "n_weighted", "pDeath")]

kableExtra::kable(res)

rm(res)

```







Finally, we will compare the injury profiles and case mortality rates, stratified by age group (50-65, 66-80, and >80) and  mechanism of injury group.

```{r injury profiles and mortality by age group and mechanism}



mdata %>%
	group_by(age_group, mech1) %>%
	summarise(n_obs = n(),
						n_weighted = round(sum(discwt, na.rm = T)), 
						age = med_iqi(age, w = discwt),
						female = round(my.weighted.mean(female, w = discwt)*100, 2),
						mortality = round(my.weighted.mean(mortality, w = discwt)*100, 2),
						pDeath = med_iqi(pDeath*100, w = discwt)) %>% 
	ungroup() %>%
	kableExtra::kable()


```


\
\
\
\

https://m-clark.github.io/posts/2019-10-20-big-mixed-models/#additive-models-as-mixed-models
```{r mixed model}
library(mgcv)
library(gammit)


```













```{r}
pander::pander(sessionInfo())
```

